### 2017-03-29 paper/evaluation.tex
pass on text and added subjects piechart

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts.
Figure~\ref{fig:subject-query} illustrates the query as an HTTP
request.

@@

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of March 25th 2017, our search criteria returned
\SubjectsGithub{} subjects.  From the \SubjectsGithub{} downloaded
projects, \SubjectsGithubNotMaven{} were not Maven projects (or did
not have a \pomf{} in the root directory) and
\SubjectsGithubNotTestable{} were in an untestable revision (\eg,
missing dependencies or incompatible testing environment). To ensure
that our sample set is stable, we retested the remaining subjects to
eliminate flaky tests (total of \SubjectsGithubFlaky{} subjects). Our
final set consists in \numSubjs{} testable subjects.

@@

To run our experiments, we used a Virtual Machine with four cores and
4 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit version).
Software settings include \Comment{the Linux \emph{sysstat} package
to measure performance, }git to fetch subjects, Java 8 and Maven
3.3.9 to build and test subjects. Our evaluation scripts depends on
Python 3.4 and Bash to execute and R to analyze the data.
For replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}

>>>>

On \github{}, when a user adds a star to a project, s/he demonstrated
appreciation and bookmarked it for later
reference~\cite{github-stars}.  Although there is not a specific range
for the number of stars, our criteria is an estimation to avoid
trivial subjects: we assumed that \github{} users are likely to
demonstrate interest on well-tested projects. The third criteria is a
constraint to skip projects without recent activity. The fourth
criteria is an approximation to find projects with Maven support. The
rationale is that if the string \emph{mvn} exists in the \emph{readme}
file, it may represent a Maven call (\eg, to compile or test the
project). We used Maven as a reference due to its popularity on Java
projects and to automate our evaluation scripts. A Maven project may
contain several sub-modules with multiple \pomf{} files. We considered
only projects with a \pomf{} file located in the root directory.
Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.

@@

As of March 25th 2017, our search criteria returned \SubjectsGithub{}
subjects. Figure~\ref{fig:subjects} summarizes our sample set. From
the \SubjectsGithub{} downloaded projects, \SubjectsGithubNotMaven{}
were not Maven projects (or did not have a \pomf{} in the root
directory) and \SubjectsGithubNotTestable{} were in an untestable
revision (\eg, missing dependencies or incompatible testing
environment). To ensure that our sample set is stable, we retested the
remaining subjects to eliminate flaky tests (total of
\SubjectsGithubFlaky{} subjects). Our final set consists in
\numSubjs{} testable subjects.

\vspace{-3ex}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.25\textwidth]{plots/subjects/subjects.pdf}
    \caption{\label{fig:subjects}\Fix{this is mocked data!}}
\end{figure}
\vspace{-2ex}

@@

To run our experiments, we used a dedicated server with eight cores
and 16 GB of memory, running Ubuntu 14.04 LTS Trusty Tahr (64-bit
version).  Software settings include \Comment{the Linux \emph{sysstat}
package to measure performance, }git to fetch subjects, Java 8 and
Maven 3.3.9 to build and test subjects. Our evaluation scripts depends
on Python 3.4 and Bash to execute and R to analyze the data.  For
replication, all source artifacts are publicly available at
\Fix{create gh-pages}, including supporting scripts (\eg, the script
that test subjects and generates the raw data), and the full list of
projects. \Comment{, and a \emph{Vagrantfile} to emulate our hardware
and all software dependencies.}
